Open Clusters Characterization in Gaia DR2 Using ML Algorithms

### 2020-11-12 thesis/thesis.tex
thesis: Expand Introduction chapter

%% TODO: 1.1 Motivation

@@

%% TODO: 1.2 Planteamiento

@@

%% TODO: 1.3 Estructura de la memoria

@@

@@

The main aim of this thesis is to \emph{build an unsupervised clustering model for open cluster characterization}.
This model must be \emph{non-supervised non-parameterized}, and has to be valid for a wide range of open clusters.

>>>>

% TODO: 1.1 Motivation

@@

% TODO: 1.2 Planteamiento

@@

% TODO: 1.3 Estructura de la memoria

@@

Stars that belong to a same OC share relative positions, so their parallax value is similar among them. They also share similar values of
proper motion, both in right ascension and declination. Another property, since these stars were born from the same gas cloud and at the same
temporary stage, their metallicity must be uniform. However, to take into account this last property, we face the inconvinient that this
parameter is not directly available in Gaia DR2 database. We will avoid this issue by looking at $E(b-r) / G_{mag}$ diagrams with well
defined isochrone curves \cite{bressan2012parsec}. These isochrone curves are derived from theoretical models that mainly involve metallicity
and mass/brightness from stars. With these models we can define important properties for the development of stars and their evolution in the
H-R diagram. Examples of these curves are shown in Figure \ref{fig:examples_of_isochrones}.

Again, since these stars were born close in time, regarding their intrinsic properties (mass/brightness), these stars must present a very
well defined and sharp profile with low sparsing through the main sequence in the H-R diagram.

We will take advantage of these properties to validate that the open clusters obtained are right.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/theoretical_isochrones_in_hr_diagrams.pdf}
  \caption{Examples of theoretical isochrones in the HR diagram taken from \protect\citeA[p.~16]{bressan2012parsec}}
  \label{fig:examples_of_isochrones}
\end{figure}

@@

The main aim of this thesis is to \emph{build an unsupervised clustering model for open cluster characterization}.

We want this model to be \emph{non-supervised non-parameterized} in order to fit a wide range of clusters without
the need of fine tunning hyperparameters regarding the topology or size of the studied clusters.
